Figures

### 2019-06-21 figures/07_model-selection.Rmd
towards coefficient summary fig

>>>>

```{r model_summary, echo=FALSE}
fit_tp <- re_brms[[3]] # 3 is best tp model with re effects

# plot(fit_tp)

gg_tp <- spread_draws(fit_tp, 
                     b_maxdepth, 
                     b_hu12vbaseflowvmean, 
                     b_phosphorusvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  ggplot(aes(x = value)) +
  geom_histogram(alpha = 0.8) +
  theme_cowplot() +
  xlab("") + ylab("") +
  facet_wrap(~key, nrow = 1, scales = "free")

# summary(fit_tn)

spread_draws(fit_tn, 
                     b_maxdepth, 
                     b_soilvorgvcarbon, 
                     b_nitrogenvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = factor(key, levels = c("b_maxdepth", 
                     "b_soilvorgvcarbon", 
                     "b_nitrogenvfertilizervuse", 
                     "b_buffervcultivatedvcrops"))) %>%
  ggplot(aes(x = value)) +
  geom_histogram(alpha = 0.8) +
  theme_cowplot() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank()) +
  xlab("") + ylab("") +
  facet_wrap(~key, nrow = 1, scales = "free")

plot_grid(gg_tp, gg_tn, nrow = 2)
